### 2021-10-20 paper/output/document/paper32.tex
finished metaethical test

      As my final metaethical test, I will test that an action is either obligatory, permissible, or 
      prohibited.%
\ ob{\isacharunderscore}perm{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}P\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\isamarkupcmt{This test passes.%

@@

%:%958=488%:%
%:%959=489%:%
%:%968=491%:%
%:%980=493%:%
%:%981=494%:%
%:%982=495%:%
%:%983=496%:%
%:%987=498%:%
%:%988=499%:%
%:%990=501%:%
%:%991=501%:%
%:%992=502%:%
%:%993=503%:%
%:%994=503%:%
%:%995=504%:%
%:%998=505%:%
%:%1002=505%:%
%:%1003=505%:%
%:%1004=505%:%
%:%1006=506%:%
%:%1007=507%:%
%:%1017=509%:%
%:%1018=510%:%
%:%1019=511%:%
%:%1020=512%:%
%:%1021=513%:%
%:%1022=514%:%
%:%1023=515%:%
%:%1024=516%:%
%:%1025=517%:%
%:%1026=518%:%
%:%1027=519%:%
%:%1028=520%:%
%:%1029=521%:%
%:%1030=522%:%
%:%1031=523%:%
%:%1033=525%:%
%:%1034=525%:%
%:%1035=526%:%
%:%1036=527%:%
%:%1037=528%:%
%:%1038=528%:%
%:%1040=528%:%
%:%1044=528%:%
%:%1045=528%:%
%:%1047=529%:%
%:%1048=530%:%
%:%1049=531%:%
%:%1050=532%:%
%:%1051=533%:%
%:%1052=534%:%
%:%1062=536%:%
%:%1063=537%:%
%:%1064=538%:%
%:%1065=539%:%
%:%1069=541%:%
%:%1070=542%:%
%:%1071=543%:%
%:%1073=545%:%
%:%1074=545%:%
%:%1075=546%:%
%:%1076=546%:%
%:%1078=547%:%
%:%1079=548%:%
%:%1080=548%:%
%:%1081=549%:%
%:%1082=550%:%
%:%1083=550%:%
%:%1084=551%:%
%:%1087=552%:%
%:%1091=552%:%
%:%1092=552%:%
%:%1094=553%:%
%:%1095=554%:%
%:%1096=555%:%
%:%1106=557%:%
%:%1107=558%:%
%:%1108=559%:%
%:%1109=560%:%
%:%1111=562%:%
%:%1112=562%:%
%:%1113=563%:%
%:%1115=563%:%
%:%1119=563%:%
%:%1120=563%:%
%:%1122=564%:%
%:%1130=564%:%
%:%1131=565%:%
%:%1132=566%:%
%:%1133=566%:%

@@

%:%1136=567%:%
%:%1140=567%:%
%:%1141=567%:%
%:%1143=568%:%
%:%1153=570%:%
%:%1154=571%:%
%:%1155=572%:%

>>>>

      Next, I will test that an action is either obligatory, permissible, or 
      prohibited.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ ob{\isacharunderscore}perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\ w\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}P\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ simp\isanewline
%
\isamarkupcmt{This test passes.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
I also expect obligation to be a strictly stronger property than permissibility. Particularly, 
if A is obligated, then A should also be permissible.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{This test fails in Kroy's interpretation!
\color{blue}Nitpick found a counterexample for card i = 2 and card s = 1:
    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}%

@@

%:%959=488%:%
%:%960=488%:%
%:%961=489%:%
%:%962=490%:%
%:%963=490%:%
%:%965=490%:%
%:%969=490%:%
%:%970=490%:%
%:%972=491%:%
%:%973=492%:%
%:%974=493%:%
%:%975=494%:%
%:%976=495%:%
%:%999=501%:%
%:%1000=502%:%
%:%1001=503%:%
%:%1002=504%:%
%:%1011=506%:%
%:%1023=508%:%
%:%1024=509%:%
%:%1025=510%:%
%:%1026=511%:%
%:%1030=513%:%
%:%1031=514%:%
%:%1033=516%:%
%:%1034=516%:%
%:%1035=517%:%
%:%1036=518%:%
%:%1037=518%:%
%:%1038=519%:%
%:%1041=520%:%
%:%1045=520%:%
%:%1046=520%:%
%:%1047=520%:%
%:%1049=521%:%
%:%1050=522%:%
%:%1060=524%:%
%:%1061=525%:%
%:%1062=526%:%
%:%1063=527%:%
%:%1064=528%:%
%:%1065=529%:%
%:%1066=530%:%
%:%1067=531%:%
%:%1068=532%:%
%:%1069=533%:%
%:%1070=534%:%
%:%1071=535%:%
%:%1072=536%:%
%:%1073=537%:%
%:%1074=538%:%
%:%1076=540%:%
%:%1077=540%:%
%:%1078=541%:%
%:%1079=542%:%
%:%1080=543%:%
%:%1081=543%:%
%:%1083=543%:%
%:%1087=543%:%
%:%1088=543%:%
%:%1090=544%:%
%:%1091=545%:%
%:%1092=546%:%
%:%1093=547%:%
%:%1094=548%:%
%:%1095=549%:%
%:%1105=551%:%
%:%1106=552%:%
%:%1107=553%:%
%:%1108=554%:%
%:%1112=556%:%
%:%1113=557%:%
%:%1114=558%:%
%:%1116=560%:%
%:%1117=560%:%
%:%1118=561%:%
%:%1119=561%:%
%:%1121=562%:%
%:%1122=563%:%
%:%1123=563%:%
%:%1124=564%:%
%:%1125=565%:%
%:%1126=565%:%
%:%1127=566%:%
%:%1130=567%:%

@@

%:%1135=567%:%
%:%1137=568%:%
%:%1138=569%:%
%:%1139=570%:%
%:%1149=572%:%
%:%1150=573%:%
%:%1151=574%:%
%:%1152=575%:%
%:%1154=577%:%
%:%1155=577%:%
%:%1156=578%:%
%:%1158=578%:%
%:%1162=578%:%
%:%1163=578%:%
%:%1165=579%:%
%:%1173=579%:%
%:%1174=580%:%
%:%1175=581%:%
%:%1176=581%:%
%:%1177=582%:%
%:%1179=582%:%
%:%1183=582%:%
%:%1184=582%:%
%:%1186=583%:%
%:%1196=585%:%
%:%1197=586%:%
%:%1198=587%:%
